\section{Future directions} 

For my doctoral work, I performed research investigating the mechanoregulation of cytotoxic T lymphocyte killing. Together, we found that CTLs form synaptic actin protrusions against target cells \cite{Tamzalit2018}. This act sensitizes the target cell to perforin lysis and granzyme entry, heightening the overall cytotoxic effector response. This potentiation is molecularly controlled by the actin nucleation promoting factors WASP and WAVE2, which are concentrically organized (from the center to the periphery, respectively). WASP promotes central actin protrusions associated with lytic granule fusion and content release, while WAVE2 is linked with peripheral actin protrusions and robust conjugate formation. Phenotypically, the increased application of force against targets is associated with an overall better effector response. This biomechanical force-effector relationship again appears in our model of degranulation, in which T cells use mechanical signals via integrins to home their lytic granules towards synaptic 'hotspots' in a novel manner that is distinct from their canonical signaling capacity through focal adhesions. These synaptic sites of granule fusion are immunologically verified to be foreign and accordingly sensitized to perforin. Although our data is supports this model and is in line with published work in the field, there are key outstanding questions to be answered. A discussion of some of these questions and how the results of my thesis work might inform future studies follows.

\subsection{Integrin focal adhesions}
We established a necessary mechanical requirement for integrin-mediated degranulation. Other molecules Vinculin is a stabilizing 

- Different antigen sensitivities - TCR signal strengh - \cite{Shakiba2021}

- valency or sensitivity of integrins? Minimal number needed for degranulation?

- Speculate on particular moleucles or signaling axes

- How do integrin focal adheisons isgnal to fusion machinery? How do integrins speak to the centrosome?

- Are there local lipid domains at regions of integrin mechanosensitivity? https://rupress.org/jcb/article/221/1/e202112057/212925/Thank-ORP9-for-FFAT-With-endosomal-ORP10-it-s

- Importance of mechanobiology in developmental biology

- Other speculative integrins

- Other speculative functions that mechanical activity can contribute to

\subsection{Optimizing degranulation to escape T cell suicide}
The observation that T cells tend to granulate at pillar tops (see Figure \ref{fig:fig2degranulation}) aligns with existing knowledge in the field that lytic granules require actin hypodense/cleared regions for membrane fusion \cite{Ritter2015}.  However, the transient burst of f-actin associated with the moment of degranulation (Figure \ref{fig:fig2degranulation}) is ripe to consider.  It could be associated with a burst of local mechanopotentiating synaptic force,  generating actin-flow mediated traction force to potentiate integrin granule homing (Figure \ref{fig:fig4model}). It could also be involved in actively polymerizing f-actin polymers, creating actin-rich micro-protrusions/structure at a resolution scale below detection via confocal microscopy. FRET-based actin polymerization probes could be used to interrogate if T cells were creating microdomains of actin polymerization at sites of degranulation,  as Lifeact-GFP only detects mature f-actin.  Other strategies involve photobleaching f-actin and watching its recovery (fluorescence recovery after photobleaching, or FRAP) \cite{Simon1988} relative to where cells degranulate, or using a fluorescent WASP, WAVE2, or Arp2/3 probe to monitor the relative location of actin nucleation promoting factors to lytic granule secretion \cite{Obino2016, Tamzalit2018}. 

Additional cytotoxic benefits may also be realized by degranulating at the base of actin-rich protrusions. Given the the concave orientation of the protrusion 'pit' relative to the corresponding target cell surface, we hypothesize that the perforin molecule preferentially binds to convex lipid membrane curvatures, due to its the  asymmetric, "key-like" sterics \cite{Law2010}. We could directly test this hypothesis by adapting gramicidin-based techniques from studies on fluorescence-based small unilamellar vesicles (SUVs) \cite{Ingolfsson2010,  Polozov2001}. Lipids will be constituted in buffer containing the fluorophore 8-Aminonaphthalene-1,3,6-Trisulfonic Acid (ANTS) and one of its quenchers p-Xylene-Bis-Pyridinium Bromide (DPX) to reform into large multilamellar vesicles (LMVs). Preference for convexity will be tested by treating the fluorescent SUVs with perforin, triggering oligomerization with calcium in the reaction buffer, and then measuring the amount of liberated fluorescence as a marker for pore formation. We expect the group in which perforin engages a convex lipid membrane to liberate more fluorophore than the group in which perforin engages a concave lipid membrane. Preference for concavity will be tested by constituting perforin into SUVs and triggering oligomerization and fluorophore leakage using A23187, a small molecule calcium ionophore (this ionophore can similarly be added to the convexity sample for full control).  Should it bear out that perforin has a preference for convex lipid membranes, it might potentially explain how T cells avoid being killed by their own secreted perforin, which remains an outstanding question in the field.

\subsection{SNARE proteins}
SNARE proteins are a large family of proteins that are responsible for mediating vesicle fusion and are directly responsible for the fusion of lytic granules \cite{Chang2017}.  SNARE proteins are localized to the vesicle membrane or target membranes and are called v- and t-SNARES, respectively \cite{Yoon2018}. Synaptobrevin2 is the v-SNARE and syntaxin11 is the t-SNARE that mediates lytic granule fusion in cytotoxic lymphocytes \cite{Halimani2014, Chitirala2019, Matti2013}. The Habc domain of the Q-SNARE domain folds back and allows the interaction between the v-SNARE and the t-SNARE, forming a \textit{trans-}SNARE complex \cite{Yoon2018}.  The SNARE activating function is regulated by Munc18 \cite{Spessott2017, Yoon2018, Baker2015}. Finally, the R-SNARE binds to the trimeric complex, forming a mature SNARE complex that works as a molecular zipper to bring the vesicle and plasma membranes closer together for fusion \cite{Agostino2017}.

It is likely that the finely tuned LFA-1 mediated mechanical homing of degranulation is communicated to the t-/v-SNARE complex, as SNARE complexes themselves are mechanosensitive \cite{Risselada2020}. One group observed that neuronal SNARE complexes placed under tension (around 10 pN) can maintain a partially-assembled form in which the v- and t-SNARES are in a 'frayed' state \cite{Zhou2017}. The observed mechanoregulation of SNARE complexes suggests that their mechanical activity can lead to increased biological activity (higher formation of the fusion stalk and vesicle fusion), but has yet to be directly tested in immune/T cells. There are reports of functional associations between the SNARE complex and integrin-mediated recycling at the membrane \cite{Riggs2012, Zhuang2020, Nagy2009}, but whether or not any signaling molecules liase in-/directly between the two signalosomes remains unclear and would be a fecund area for future study. 

To investigate possible integrin mechano-crosstalk to the SNARE complex, we could investigate the Munc-family group of proteins, known regulators of t-/v-SNARE fusion \cite{Ma2011, Yoon2018}. Two possible candidates to study are Munc13-1 and Munc18-1 proteins, which are in direct control of the assembly of SNARE complex components \cite{Diao2010} and have been studied extensively in neuronal synapses. In neurons, Munc18-1 activity is directly regulated by diacylglycerol and PKC$\theta$, bearing two PKC$\theta$ phosphorylation sites that, when phosphorylated, induces fusion of vesicles bearing neurotransmitters \cite{Genc2014, Nagy2009, Korogod2007}. Munc13-1 bears a C1 diacylglycerol binding domain \cite{Song1999} and markedly accelerates the kinetics of this interaction and vesicle fusion \cite{Ma2011, Song1999}. Whether or not outside-in signaling from integrins affects SNARE fusion could be tested by knocking out talin in T cells (using the gRNA we characterized in Chapter \ref{chap:chapter3}) profiling the phosphorylation of the Munc18-1 protein against T cells transduced with a non-targeting control gRNA. Additionally, one could track the localization of integrins and Munc13-1 at the synapse (using fluorescent probes) in response to a photoactivated TCR \cite{Huse2007}, which is known to induce diacylglycerol localization \cite{Quann2009}. If there is crosstalk, photoactivation of the TCR should induce integrin localization. One could even test the mechanical strength's influence over Munc13-1 (and by proxy, SNARE localization) by generating photoactivatable agonists on peptides of different TCR signal strengths (i.e. different primary sequences), which are known to induce different mechanical strengths \cite{VanderMerwe2001, Ma2010, Ma2012, Lanzavecchia1999}. These experiments would be illuminating to see if mechano-regulation of integrins directly affects SNARE complex formation and function for lytic granule fusion.

\section{Conclusion}

This study attempted to comprehensively cover the mechanobiology of cytotoxicity (Chapter \ref{chap:chapter2}) and lytic granule secretion (Chapter \ref{chap:chapter3}), which are important but still ultimately only one region of the T cell field of study. What follows is an informed discussion of mechanobiology as it pertains to \textit{other} T cell fields of study,  and how the author speculates how the field of mechanobiology might change in the years to come.

\subsection{On CTL force dynamics at the population-scale}

Going forward, it would be interesting to investigate dynamics of synaptic force exertion in a single CTL against a target cell. In particular, one wonders if the CTL at first pass deploys a standard range of force exertion and protrusion-type or cellular structure (in a "probing phase"), and then must dynamically change its range of force exertion or arsenal of structures for force exertion according to local biostructural architecture (i.e. what is the lifetime force action of a standard CTL encounter?). Certainly these events are correspondingly influenced by the signaling molecules present at the synapse, each of which live their own biophysical lives by mere virtue of their presence. Answering such questions would require direct interrogation of a live CTL-target cell synapse. Previous technologies for measuring membrane tension include atomic force microscopy or an optical trap - but both remain insufficiently precise to monitor real-time \textit{in vitro} or \textit{in vivo} synapse dynamics. Certain fluorescence-based technologies have been recently been developed in order to measure synapse dynamics that ignore restrictive planar geometries \cite{Vorselen2020}. Combined with fluorescent probes, the use of these microparticles could elucidate "phases" of the T cell physical response as it (putatively) probes, adheres, degranulates, kills, and releases, the target cell.

Thinking outside the context of single-T cell force exertions, it would be fascinating to investigate the host CTL-ome at large, if certain "battalions" or "legions" of CTLs exist, organized according to their physical strengths and effector capabilities. Certainly a reasonable first-pass method of organization is expression levels of certain effector genes and molecules (e.g. \textit{Prf}, \textit{Grzb}, \textit{Ifng}), but these measures obviously omit the  mechanoregulation of these molecules and thus miss their effects in totality. One would require  experimental techniques capable of not only measuring single-cell T cell force exertion \textit{en masse}, but also the possible swarm behavior of responding T cells in which an initial "less capable" group of T cells is replaced by stronger effector cells (or weaker, in a "clean up" phase). Certain molecular perturbation platforms that are designed to measure CRISPR-based perturbations at the protein level \cite{Wroblewska2018} come closer to characterizing all of the effects that a molecular perturbation truly encompasses. Other platforms for monitoring infiltrating immune cells into locally perturbed regions of the tumor microenvironment also exist \cite{MaximeDhainaut2021}. One could imagine choosing a tumor system for this platform that has been spatially perturbed heterogeneously for known cytoskeletal/cell stiffness molecules and investigate how T cells of well-characterized strengths segregate (and presumably kill). Characterizing T cell swarm or group behavior would be a massive undertaking that would take many years to perform.

Many of the experiments conducted in order to complete this doctoral thesis were performed using \textit{in vitro} systems. These systems were designed to interrogate force activity by holding the force threshold constant (e.g. micropillars, DNA membrane tension probes), while observing the cell's force activity in time. While these arrangements are useful for ease of investigation, holding constant a variable as broad as the force threshold creates major scientific blind spots even in real-time studies (much less bulk studies via co-culture assays). This is true particularly in studies focused on the effector cell, in which the arrangement ignores half of the cellular conversation: the target cell \cite{Tello-lafoz2021}. The target cell is capable of dynamically responding to the effector cell's efforts to kill (presumably in a cooperative or antagonistic manner), which is entirely neglected in these experimental systems. 

\subsection{On the mechanobiology of exhausted T cells}

To date, there has been no direct study of mechanobiology of exhausted T cells. Nevertheless, given what we know about the immunological behavior of exhausted T cells and how mechanobiological principles influence these behaviors in other T cell contexts (such as na{\"i}ve, proliferating, or activated T cells), we can comfortably speculate on how we might think mechanical principles might influence exhausted T cell (dys)function.

The label 'exhausted T cells' can be quite wide, but general agreement can be found in a definition that includes a molecular signature of increased inhibitory receptor expression, such as B lymphocyte induced maturation protein 1 (Blimp-1), basic leucine zipper transcription factor, ATF-like (BATF), nuclear factor of activated T cells (NFAT), T-box expressed in T cells (T-bet), eomesodermin (Eomes), and PD-1 (programmed cell death protein 1) \cite{Wherry2011, Quigley2010, Keir2008, Doering2012, Wherry2007, Wang2012,  Lazarevic2013, Rangachari2012, Shin2009, Paley2012, Larsson2013}. In particular, exhausted T cells are strongly associated with a $PD-1^{hi}$ phenotype \cite{Keir2008}. Persistent antigen stimulation in the context of chronic infection triggers epigenetic alternations to the \textit{Pdcd1} locus, resulting in this higher surface expression of the PD-1 inhibitory receptor. The PD-1/PD-L1 signaling axis is known to attenuate TCR activation \cite{Mizuno2019}, proliferation \cite{Schietinger2014}, and T cell migration \cite{Zinselmeyer2013}. Although direct evidence is needed, it seems reasonable to suggest that exhausted T cells might display diminished physical capacity, further dampening their effector capabilities.

TCR mechanical signaling is a known requirement for T cell activation \cite{Hu2016}.

Exhausted T cells also present a diminished metabolic state. Accordingly, it is likely that their effector capacity is severely weakened, considering that cytoskeletal remodeling is a highly energy intensive activity. Reports on the energy dynamics of actin-polymerization inhibited cells indicate that ATP consumption is up to 50\% slower \cite{Bernstein2002, Ahmed2015}. Depletion of glucose/ATP from the medium also immobilizes the motor protein myosin \cite{Xu2014}, which is known to be involved in potentiating lytic granule fusion \cite{Basu2016}.

\subsection{On the mechanobiology of engineered T cells}

Despite the intense global research effort in developing novel cancer immunotherapies, a major dimension of the interactions between cancer and the immune system, its biomechanical aspect, has been largely underappreciated. Throughout their lifecycle, T cells constantly survey a multitude of organs and tissues and experience diverse biomechanical environments, such as shear force in the blood flow and a broad range of tissue stiffness. Furthermore, biomechanical properties of tissues or cells may be altered in disease and inflammation. Biomechanical cues, including both passive mechanical cues and active mechanical forces, have been shown to govern T cell development, activation, migration, differentiation, and effector functions. In other words, T cells can sense, respond to, and adapt to both passive mechanical cues and active mechanical forces. Biomechanical cues have been intensively studied at a fundamental level but are yet to be extensively incorporated in the design of immunotherapies. Nonetheless, the growing knowledge ofT cell mechanobiology has formed the basis for the development of novel engineering strategies to mechanically modulate T cell immunity, a nascent field that we termed “mechanical immunoengineering”. Mechanical immunoengineering exploits biomechanical cues (e.g., stiffness and external forces) to modulate T cell differentiation, proliferation, effector functions, etc., for diagnostic or therapeutic applications. It provides an additional dimension, complementary to traditional modulation of biochemical cues (e.g., antigen density and co-stimulatory signals), to tailor T cell immune responses and enhance therapeutic outcomes. For example, stiff antigen-presenting matrices have been shown to enhance T cell proliferation independently of the intensity of biochemical stimulatory signals \cite{Lei2020}

Engineering of ligands on planar surfaces has shown thatTCR arrangement can be manipulated by external cues.It was demonstrated that focal clustering of TCR can beinhibited by presenting antigens in a hollow ring config-uration, which in turn reduces IFN-gsecretion and pro-liferation of T-cells[42]. In contrast, TCR clustering andcell signaling can be promoted by introducing multivalentareas of receptors on the activating surface[42,43]. Allthesestudies suggest that TCR clusters cancontrol T-cellresponse by their micro and nanoscale organization \cite{Aramesh2019}

The formation of CAR IS has characteristics unlike the structure of TCR IS. The CAR IS does not present a systematic bull's eye structure, which is a characteristic feature of TCR IS. Organization of the actin ring in CAR IS is poor and actin may not be not completely diminished at the center of CAR IS (22). LFA-1 is disorganized and CAR-tumor antigen complexes form microclusters that are randomly distributed at the CAR IS (23) (Figure 1B). While TCR IS requires 5–10 min to form the bull's eye structure, the CAR IS might not need to form these stable structures because the disorganized multifocal pattern of CAR IS is sufficient to rapidly induce significant proximal signaling, which occurs within a short period of time (\textless 2 min). Another important part of IS biology is the delivery of cytotoxic granules, including perforin and granzymes, to the IS mediated by microtubule organizing center (MTOC) (24). The rapid but short duration of proximal signaling of CAR IS also induces rapid MTOC migration to the IS and accelerates the delivery of granules (23). Although the mechanisms of CAR IS have gradually been revealed, it is still unclear whether the differences in CAR IS structure correlate with the efficacy of CAR T cells \cite{Li2020, Watanabe2018}.


\subsection{On nutrient mechano-sensing}

Food for thought: How cell adhesion coordinates nutrient sensing

mTORC1 activity is supported by spatial association with focal adhesions

Structural Insights into the Activation of mTORC1 on the Lysosomal Surface

\subsection{On wound healing}

Lipid peroxidation regulates long-range wound detection through 5-lipoxygenase in zebrafish

Tissue Damage Signaling Is a Prerequisite for Protective Neutrophil Recruitment to Microbial Infection in Zebrafish

\subsection{On \textit{in vitro}-based investigations}

Of course, many of these experiments were also performed using the OT-I transgene system. 

\section{\textit{La fin}}

A number of outstanding questions surrounding T cell mechanobiology remain open for investigation. These questions remain unanswered today for either knowledge or technically-based reasons, but they will surely be answered in due time.
